Paper 1: Instrument development

### 2024-10-08 Rmd/Paper1.Rmd
Added separate presentation of results in paper for easy access

```{r eval=T}
alpha(df_run2[,c("TK1", "TK2", "TK3")])
alpha(df_run2[,c("CK1", "PCK2", "PCK5", "CK5", "CK3", "CK2")])
alpha(df_run2[,c("TPK1","TPK4","TCK1","TCK4", "TPACK2","TPACK4")]) # , "TPK4"
```

@@

@@

df    <- CFA_TPACK_PST[,unlist(TPACK_PST_items[1:3])]
describe(df)      # with missing (see n)? (na.rm=TRUE)

score_TPACK <- scoreItems(TPACK_PST_items,df)
describe(score_TPACK$scores)
```

@@

# get correlation matrix of observed variables
cor_mat <- lavInspect(model_three_factor, what="cor.ov")
omega(cor_mat, nfactors=3)

@@

```{r measureQ, eval=T}
measureQ(model_three_factor, CFA_TPACK_PST)
```

>>>>

```{r eval=T}
alpha_TK <- alpha(df_run2[,c("TK1", "TK2", "TK3")])
alpha_PCK <- alpha(df_run2[,c("CK1", "PCK2", "PCK5", "CK5", "CK3", "CK2")])
alpha_TPACK <- alpha(df_run2[,c("TPK1","TPK4","TCK1","TCK4", "TPACK2","TPACK4")]) # , "TPK4"

alpha_TK
alpha_PCK
alpha_TPACK
```

@@

# Results of EFA

Here I reproduce the results presented in paper 1.

table 1

```{r}
print.psych(fa.sort(model_3factor_run2))
```

```{r}
alpha_TK$total$std.alpha
alpha_PCK$total$std.alpha
alpha_TPACK$total$std.alpha
```

@@

df_CFA    <- CFA_TPACK_PST[,unlist(TPACK_PST_items[1:3])]
describe(df_CFA)      # with missing (see n)? (na.rm=TRUE)

score_TPACK <- scoreItems(TPACK_PST_items,df_CFA)
describe(score_TPACK$scores)
```

@@

# get correlation matrix of observed variables
cor_mat <- lavInspect(model_three_factor, what="cor.ov")
observed_omega <- omega(cor_mat, nfactors=3)
observed_omega

@@

```{r measureQ, eval=T}
table.2 <- measureQ(model_three_factor, CFA_TPACK_PST)
```

# Results of CFA

Table 2

```{r}
pander(fit_table)
```

Figure 3

std.all (column to the far right) shows the standardized results used in figure 3.

```{r}
parameterEstimates(model_three_factor, standardized=TRUE)
```

Table 3

```{r}
describe(df_CFA)
```

F1 equals TPACK, F2 equals PCK and F3 equals TK. Omega_t is the first column, while omega_h is the second column.

```{r}
observed_omega$omega.group
#observed_omega$omega.group$general
#observed_omega$omega.group$total
```

Table 4

```{r}

so.lv <- NULL # temp variable second order level

cat("\n", "  Table 2. Descriptive Statistics (Observed Mean, Latent s.d., AVE, Construct Reliability, Latent Correlation)", rep("\n", 2))
rownames(table.2) <- rep("    ", nrow(table.2))
print(table.2, quote=FALSE, right=TRUE)
cat("\n", "  Note: AVE = Average Variance Extracted; * = AVE significantly lower than 0.5 (p < .05)","\n")
if (length(so.lv) == 0) {
  cat("         diagonal elements in brackets = Construct Reliability","\n")
} else {
  cat(paste0("         diagonal elements in brackets = Construct Reliability for first-order factor and ", omega, " for second-order factor"), "\n")
}
cat("         A = Construct Reliability significantly lower than 0.7; B = Construct Reliability significantly lower than 0.8 (p < .05)", "\n")
cat("         Correlation coefficient: a = significantly larger than 0.85; b = significantly larger than 0.8; c = significantly larger than 0.7 (p < .05)", "\n")
if (length(so.lv) == 0) {
  cat("         # = AVE is significantly less than squared-correlation (p < .05)", rep("\n", 3))
} else {
  cat("         # = AVE is significantly less than squared-correlation (p < .05)", rep("\n"))
  cat("         Observed mean of second-order factor is based on all items ignoring the second-order structure", rep("\n", 3))
}
```
